Convective penetration probably parameterizes convective overshoot

### 2021-07-20 manuscript/ms.tex
Added MESA details

\begin{abstract}
Most stars host convection zones in which heat is transported directly by fluid motion.
Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
Here we present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
We compare this theory to 3D numerical simulations using a simplified Boussinesq model of stellar convection.
Although it can take thousands of overturn times to develop, in all cases we find significant convective penetration.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
We discuss prospects for extending these results to more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}

%%%% Body of paper
\section{Introduction}
\label{sec:introduction}

\subsection{Context}
Convection is a crucial mechanism for transporting heat in stars~\citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
For example, convection drives the magnetic dynamo of the Sun, leading to a whole host of emergent phenomena collectively known as solar activity \citep{brun_browning_2017}.
Convection also mixes chemical elements in stars, which can modify observed surface abundances or inject additional fuel into their cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
Furthermore, convective motions excite waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure and evolution, and for connecting this understand to observations.

@@

The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes \citep{zahn1991, brummell_etal_2002, korre_etal_2019}.
The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
The primary focus of this work is convective penetration.

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Vertical slice through a simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
(Left) Vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly at the top of the penetration zone where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations, normalized by their average magnitude at each height to clearly display all dynamical features.
%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure*}

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
While a link between stiffness and entrainment and overshoot processes has seemingly emerged in previous work, a mechanism for penetration remains elusive.

Studies which more closely model the conditions inside of stars have presented confusing results.
Many studies have exhibited hints of penetrative convection -- that is, the mixing of the entropy towards an adiabatic profile beyond the convective boundary.
Some of these studies exhibit dynamical or flux-based hints of penetration (the convective flux is negative and the radiative flux carries more than the total flux going through the simulation), but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}
Others report a change of the entropy gradient towards the adiabatic beyond the convecting region \citep{hurlburt_etal_1994, saikia_etal_2000, rogers_etal_2006, kitiashvili_etal_2016}
Some simulations show little evidence of true penetration \citep[see e.g., the superadiabaticity profiles of][]{higl_etal_2021}.
These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

There are hints in the literature that convective penetration may be dependent upon energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this idea, and found that penetration lengths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

\subsection{Convective penetration \& this study's findings}

Convective penetration is the process by which convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient to be nearly adiabatic.
\begin{quote}
\emph{
In this paper, we present simulations which exhibit convective penetration.
}
\end{quote}
This process is phenomenologically described in Sec.~\ref{sec:central_results}.

In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration length can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.

\section{Central Result: Convective Penetration}
\label{sec:central_results}

In Fig.~\ref{fig:vertical_dynamics_panels}, we display a snapshot of dynamics in an evolved simulation which exhibits convective penetration.
The simulation domain is a 3D Cartesian box, and this figure shows a vertical slice through the center of the domain.
In the left panel, we display the vertical velocity.
We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the temperature gradient departs from adiabatic towards the radiative gradient.
In the right panel, we display temperature perturbations away from the time-evolving mean temperature profile.
We see that warm upwellings in the Schwarzschild-unstable convection zone (below the dashed line) become cold upwellings in the penetration zone (above the dashed line), and these motions excite gravity waves in the stable radiative zone (above the solid line).

We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
The radiative gradient $\gradrad$ is shown in orange.
The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).

Our goals in this paper are to understand how these PZs form, and to parameterize this effect so that it can be included in 1D stellar evolution calculations.

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{grad_profiles.pdf}
\caption{
Horizontally- and temporally-averaged profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
\label{fig:grad_profiles}
}
\end{figure}

\section{Theory}
\label{sec:theory}
In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the convection and penetration zones.
In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
We find that excess KE in the convection zone can cause a penetration zone to form.
By balancing the excess KE in the convection zone with a buoyancy-braking work term in the PZ, we are able to derive the size of the PZ.
We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

Assuming convection reaches a time-stationary state, the heat fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
The mean temperature profile $\overline{T}$ carries the radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the temperature gradient and radiative temperature gradient 
\begin{equation}
\justgrad \equiv -\partial_z \bar{T} \qquad
\gradrad \equiv \frac{\bar{\Ftot}}{k}.
\label{eqn:gradrad_definition}
\end{equation}
We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
Marginal stability is achieved when $\justgrad = \gradad$, which we take to be a constant.
We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

The addition of a nonzero $\gradad$ to Eqn.~\ref{eqn:temperature} was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but in this incompressible model where there is no density stratification to break the symmetry of upflows and downflows precisely the same arguments can be applied to the inverted problem.

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
Temporally- and horizontally-averaged profiles in an evolved simulation from the kinetic energy equation (Eqn.~\ref{eqn:kinetic_energy_1D}).
The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
\label{fig:theory_profiles}
}
\end{figure}

>>>>

\begin{abstract}
Most stars host convection zones, in which heat is transported directly by fluid motion.
Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
Here we examine how convective motions mix entropy and in turn extend the size of the convection zone, a process referred to as convective penetration.
We derive a ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we construct a model of penetration based on an energy balance, and find that the extent of penetration is controlled by $\mP$.
We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
We further discuss prospects for extending these results to more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}

%%%% Body of paper
\section{Introduction}
\label{sec:introduction}
Convection is a crucial mechanism for transporting heat in stars~\citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
For example, convection drives the magnetic dynamo of the Sun, leading to a whole host of emergent phenomena collectively known as solar activity \citep{brun_browning_2017}.
Convection also mixes chemical elements in stars, which can modify observed surface abundances or inject additional fuel into their cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
Furthermore, convective motions excite waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure and evolution, and for connecting this understand to observations.

@@

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
We are interested in the case where there are no composition gradients, and where the flux driving the convection is constant over long timescales.
We are therefore not focused on the mechanisms by which convection zones grow \citep[e.g., entrainment, ][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}, but rather the extent of saturated, statistically-stationary convective regions.

Convective overshoot and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Experiments exhibiting extensive convective penetration have a long history \citep[dating back to e.g.,][]{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Modern experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Some recent studies in simplified Boussinesq setups suggest that the penetration depth is highly dependent on the stiffness \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
Many studies of density-stratified convective atmospheres find significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, dietrich_wicht_2018}.
However, some studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
Many modern simulations utilize stellar structure models as background states and find significant convective overshoot and/or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but the precise results of past studies are often contradictory and no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

There are hints in the literature that convective penetration may be dependent upon energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

In this work, we design two numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
We use a modified incompressible, Boussinesq model to study the simplest possible system, and derive theoretical predictions for the size of the penetrative zone.
We test this theory using 3D numerical simulations.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and derive predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.

\section{Theory}
\label{sec:theory}

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the gradient and radiative gradient 
\begin{equation}
\justgrad \equiv -\partial_z \bar{T} \qquad
\gradrad \equiv \frac{\bar{\Ftot}}{k}.
\label{eqn:gradrad_definition}
\end{equation}
We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
Marginal stability is achieved when $\justgrad = \gradad$, a constant.
We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

The addition of a nonzero $\gradad$ to Eqn.~\ref{eqn:temperature} was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but the same logic applies to the inverted problem.

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}
\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{theory_profiles.pdf}
\caption{
(left) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in a simulation. 
$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
(middle) Measured profiles of $\justgrad$ (green) compared to $\gradad$ (grey, a constant) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
\label{fig:theory_profiles}
}
\end{figure*}

Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+ \frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= 1 - f,
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
This is mathematically equivalent to standard boundary-driven convection experiments.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).
